Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
add changes removed by commit 5b26520
write concluding paragraph

\begin{table}
\begin{center}
\begin{tabular}{lcl}
& Acc. \%  &  \multicolumn{1}{c}{Design}  \\
\cite{olivetti2013wonder} OE & 17 & compression distance, random forests \\
\cite{elizalde2013vector} ELF & 55 & i-vector, LDA \\
\cite{krijnders2013tone} KH & 55 & cochleogram, SVMs \\
\cite{patil2013multiresolution} PE & 58 & 2D Gabor filters, SVMs \\
\cite{lee2013acoustic} NHL & 60 & UL of mel spectra, SVMs \\
\cite{nogueira2013sound} NR1 & 60 & MFCCs and ILD features, SVMs \\
\cite{chum2013ieee} CHR & 65 & sparsity features, HMMs  \\
\cite{geiger2013large} GSR & 69 & Mel-frequency Spectra and MFCCs, SVMs \\
\cite{rakotomamonjy2015histogram} RG & 69 & histogram of gradient (HOG), SVMs \\
\cite{li2013auditory} LTT & 72 & MFCCs, tree baggers \\
\cite{roma2013recurrence} RNH & 76 & RQA features stacked with MFCCs, SVMs \\
\hline

\end{tabular}
\end{center}
\caption{Algorithms evaluated on the DCASE2013 ASC private DCASE2013 dataset. RQA stands for recurrence quantification analysis, ILD for inter-aural differences and UL for unsupervised learning. Algorithms above the horizontal line participated to the DCASE challenge. Others used the private dataset afterward.  \label{tab:dcase}}
\end{table}

@@

\section{Feature design}
\label{sec:design}

Before supervised or unsupervised classification, it is beneficial to process scattering coefficients with feature transformations that improve invariance, normality, or generalization power.
In this section, we review three ways of achieving these properties, namely logarithmic compression, and temporal integration, and standardization.
Whether we adopt a time-frequency perspective or a machine learning perspective on the problem of acoustic scene classification, such operations would either be qualifies as post-processing or pre-processing.

\subsection{Logarithmic compression}
\label{sec:logcomp}

@@

\ml{Vincent: un par pour resumer la partie classif}
%, identified in the time domain in the unsupervised setting and in the features domain in the supervised case, provided that the dimensionality is sufficiently high. \ja{I'm not sure what this last part means.}

>>>>

\begin{table}
\begin{center}
\begin{tabular}{lcl}
& Acc. \%  &  \multicolumn{1}{c}{Design}  \\
\cite{olivetti2013wonder} OE & 17 & compression distance, random forests \\
\cite{elizalde2013vector} ELF & 55 & i-vector, LDA \\
\cite{krijnders2013tone} KH & 55 & cochleogram, SVMs \\
\cite{patil2013multiresolution} PE & 58 & 2D Gabor filters, SVMs \\
\cite{lee2013acoustic} NHL & 60 & UL of mel spectra, SVMs \\
\cite{nogueira2013sound} NR1 & 60 & MFCCs and ILD features, SVMs \\
\cite{chum2013ieee} CHR & 65 & sparsity features, HMMs  \\
\cite{geiger2013large} GSR & 69 & Mel-frequency Spectra and MFCCs, SVMs \\
\cite{rakotomamonjy2015histogram} RG & 69 & histogram of gradient (HOG), SVMs \\
\cite{li2013auditory} LTT & 72 & MFCCs, tree baggers \\
\cite{roma2013recurrence} RNH & 76 & RQA features stacked with MFCCs, SVMs \\
\hline
\end{tabular}
\end{center}
\caption{Algorithms evaluated on the DCASE2013 ASC private DCASE2013 dataset. RQA stands for recurrence quantification analysis, ILD for inter-aural differences and UL for unsupervised learning. Algorithms above the horizontal line participated to the DCASE challenge. Others used the private dataset afterward.  \label{tab:dcase}}
\end{table}

@@

\section{Feature design}
\label{sec:design}
\ja{It seems that what we are doing in this section is more post-processing than feature design, which would be the scattering transform itself.}

Before supervised or unsupervised classification, it is beneficial to process scattering coefficients with feature transformations that improve invariance, normality, or generalization power.
In this section, we review three ways of achieving these properties, namely logarithmic compression, and temporal integration, and standardization.
Whether we adopt a time-frequency perspective or a machine learning perspective on the problem of acoustic scene classification, such operations would either be qualifies as post-processing or pre-processing.
\subsection{Logarithmic compression}
\label{sec:logcomp}

@@

Within a supervised setting of acoustic scene classification (ASC), we have outlined the comparative benefits of log-scattering features over MFCCs, of majority voting at a mid-level time scale of $T=372\,\mathrm{ms}$ over prediction at a high-level time scale of $T=24\,\mathrm{ms}$, and of an adapted Gaussian kernel over the linear kernel in support vector machine (SVM) classification.
%, identified in the time domain in the unsupervised setting and in the features domain in the supervised case, provided that the dimensionality is sufficiently high. \ja{I'm not sure what this last part means.}
